SoK: The Evolution of Defenses Against Web Application Attacks

### 2014-11-10 docs/questioning.tex
some corrections

\begin{enumerate}
\item The number of times the corresponding publication has been cited.
\item Quadruples that show the values of true
positives ({\sc tp}), true negatives ({\sc tn}),
false positives ({\sc fp}), and false negatives
({\sc tn}). For every quadruple there is a corresponding
suffix that indicates whether the testbed was based
on: real-world applications known to be vulnerable
(r), synthetic benchmarks (s), both (a).
If no testing has taken place we add a question
mark ({\bf ?}).
\item The computational overhead of the
mechanism as stated in the publication.
\item The attacks that the mechanism detects.
\end{enumerate}

\noindent
{\sc na} (Not Available) means that a requirement is not
mentioned in the paper. {\sc nq} (Not Quantified)
indicates that a requirement is mentioned in the publication
but it is not quantified.

@@

		\item[2] For every quadruple there is a corresponding suffix that indicates whether the testbed was

@@

\subsection{Testing}

Here we comment on how the mechanisms that we
described earlier, were tested in terms of both
diagnostic and computational performance.

\subsubsection{Diagnostic Performance}

@@

\subsubsection{Computational Performance}

Table~\ref{tab:comp} shows for every mechanism its
corresponding overhead. In addition, it indicates
if the overhead is applied to the server-side ({\sc s}),
or the client-side ({\sc c}).
Our first observation, is that there is a differential
in the way in which the computational overhead of the
mechanisms is measured. In many cases, 16 out of
34 (47.05\%), the overhead is provided as a percentage
while in other cases, 7 our of 34 (20.5\%),
the authors provide the time (in terms of ms) that
their mechanisms add to the normal execution time of
the protecting entity. Surprisingly, in 10 cases (29,4\%),
the overhead was either not available ({\sc na}) or
not quantified ({\sc nq}). In the case of {\sc php aspis},
its authors indicate that with their mechanism,
the execution time is doubled.

Given the fact that the final steps of
{\sc dsl} injection and {\sc csrf} attacks take place
on the server-side, all the mechanisms that detect
such attacks are placed in some point within the server.
From the mechanisms that detect {\sc dsl} code injection
attacks, 3 out of 13 (23\%) do so at the level
of the {\sc rdbms} --- locus $\Omega$.
The other 11 wrap {\sc api} calls related to output
vectors --- locus {\sc z}.

However, in the case of frameworks that deal
with JavaScript-driven {\sc xss} attacks
we observe that attack detection may take place
either on the server-side or on the client-side.
In the first case, a proxy is placed on the server
to examine the server's responses before they
reach the user's web browser. In the second
case a modified browser or a library that
is securely downloaded from the server,
checks the responses for potential attacks.
Our findings indicate that the tendency so far,
is to create frameworks that perform detection
on the client side. In particular, 11 out of
19 frameworks (57,8\%) detect JavaScript-driven
{\sc xss} attacks at the client's side.
Note that the majority of the mechanisms that
detect such attacks on the server-side, can also
detect {\sc dsl} code injection attacks (7 out of 8).

@@

Table~\ref{tab:avail} presents our findings regarding the availability
of the mechanism in terms of source code and corresponding
executables. We also examined the availability of the testbeds
mentioned in the paper. The check mark (\tick) indicates that at some
point within the publication, there is a homepage where the reader can
refer to, to download the corresponding software. {\bf AO} (Available
On-line) suggests that the software is available on-line but the
address was not mentioned in the paper, which probably indicates that
the authors made it available after the publication. The question mark
({\bf ?}), indicates that the a homepage for the software was included
in the publication but now it is not available.

Our first observation indicates that only 6
out of 34 (17.6\%) of the authors provided a homepage for
their mechanism through their publication.
2 from these 6 homepages are currently not available.
Also, in 5 cases, authors made either the source code
or their executables available after their paper
got published. Finally, we observe that only 3
out of 34 (8.8\%) authors have currently
their testbeds available on-line.

>>>>

\begin{enumerate}
\item The number of times the corresponding publication has been cited.
\item Diagnostic Performance and Computational Overhead measurements.
\item The attacks that the mechanism detects.
\end{enumerate}

@@

      \item[2] Quadruples contain numbers given for True Positives
        ({\sc TP}), True Negatives ({\sc tn}), False Positives ({\sc
          fp}) and False Negatives ({\sc fn}). For every quadruple there is a corresponding suffix that indicates whether the testbed was

@@

@@

Table~\ref{tab:avail} presents our findings regarding the availability
of the mechanism in terms of source code and corresponding
executables. We also examined the availability of the testbeds
mentioned in the paper. The check mark (\tick) indicates that at some
point in the publication there is a homepage where the reader can
refer to, to download the corresponding software. {\bf AO} (Available
On-line) suggests that the software is available on-line but the
address was not mentioned in the paper, which probably indicates that
the authors made it available after the publication. The question mark
({\bf ?}), indicates that a homepage for the software was given in the
publication but now it is not available.

We see that only 6 out of 34 (17.6\%) of the authors provided a
homepage for their mechanism through their publication and 2 from
these 6 homepages are currently not available. In 5 cases authors made
either the source code or their executables available after their
paper got published. Regarding the availability of test materials, we
see that only 3 out of 34 (8.8\%) authors have currently their
testbeds available on-line.

Table~\ref{tab:comp} shows for every mechanism its corresponding
overhead. In addition, it indicates if the overhead is applied to the
server-side ({\sc s}), or the client-side ({\sc c}). In almost half of
the approaches, 16 out of 34 (47.05\%), the overhead is provided as a
percentage. while in other cases, 7 our of 34 (20.5\%), the authors
provide the time (in terms of ms) that their mechanisms add to the
normal execution time of the protecting entity. As they do not provide
the times of normal executions, it not possible to move from absolute
time measurements to percentage overheads. In 10 cases (29,4\%), the
overhead was either not available ({\sc na}) or not quantified ({\sc
  nq}). In the case of {\sc php aspis}, its authors indicate that with
their mechanism, the execution time is doubled.

@@

Given the fact that the final steps of
{\sc dsl} injection and {\sc csrf} attacks take place
on the server-side, all the mechanisms that detect
such attacks are placed in some point within the server.
From the mechanisms that detect {\sc dsl} code injection
attacks, 3 out of 13 (23\%) do so at the level
of the {\sc rdbms}---Locus $\Omega$.
The other 11 wrap {\sc api} calls related to output
vectors---Locus {\sc z}.

In frameworks that deal with JavaScript-driven {\sc xss} attacks we
see that attack detection may take place either on the server-side or
on the client-side. In the first case, a proxy is placed on the server
to examine the server's responses before they reach the user's web
browser. In the second case a modified browser or a library that is
securely downloaded from the server checks the responses for potential
attacks. We find that the tendency so far is to create frameworks that
perform detection on the client side: in particular, 11 out of 19
frameworks (57,8\%) detect JavaScript-driven {\sc xss} attacks at the
client's side. Note that the majority of the mechanisms that detect
such attacks on the server-side can also detect {\sc dsl} code
injection attacks (7 out of 8).
